### 2021-11-30 plos_latex_template.tex
RJ: edits to pillars and rule 1

To organize a more inclusive conference, it is necessary to identify upfront which groups of people are being excluded, the barriers that keep them from active partaking, and targeted strategies to overcome them. 
\textbf{Rule 1} is about embracing all dimensions of diversity and prioritizing the participation of groups that are often marginalized.
However, increasing diversity alone is not enough. \textbf{Rule 2} focuses on how to create a safe and welcoming environment for all the conference attendees and the larger community. 
Inclusion should start from the organizing team. \textbf{Rule 3} highlights the importance of starting with an inclusive and diverse organizing team, and provides tips on work dynamics.

@@

% Rocío: Main idea: what is diversity and why does it matter? (inequalities)
Diversity encompasses multiple dimensions: age, physical ability, career stage, gender, gender identity, geographic origin, language, neurodiversity, race, religion, sexual orientation, and socioeconomic background, to name a few.
Human diversity should be celebrated and respected in every way. Nonetheless, we live in a world with implicit hierarchies along these axes. Some statuses (\textit{e.g.}, cisgender, white, male, from North America or Western Europe) hold the privilege of being the defaults around which all systems--including conferences--are consciously and unconsciously built. \as{People outside the dominant groups suffer different forms of oppression, like sexism, racism, ableism, homophobia, and transphobia. No form of oppression operates in isolation from the others, which means some groups are particularly vulnerable and systematically left behind.}
While no isolated initiative can drastically alter conference outcomes, building a more diverse and inclusive conference starts by recognizing that these inequalities have systematically excluded whole groups of people from academia and scientific and professional circles \cite{timperleyHeMoanaPukepuke2020}. 
Recognizing this systematic exclusion, particularly in our field and in our scientific or professional community, will help identify the most marginalized and discriminated subgroups.
These are the groups that warrant deliberate efforts that ensure fair inclusion.
Investing a substantial effort towards the most excluded groups does not mean neglecting the other communities, but will instead ensure equity, guide the vision of diversity for your conference, and help design strategies to achieve it.
% vision
% back to the indicators? 
% realistic but bold (back?)
% be aware and promote awareness
%¡LAS BARRERAS!
%Express the diversity and inclusion vision for your conference by writing a diversity statement.

% Rocío: more effort towards including the more excluded
This may translate into different actions depending on your field, region, or community, \textit{e.g.}, a gender distribution of your speakers that is representative of the general population, presence of racialized people --especially Black people-- among the head organizers, speakers, and attendees, LGBTQIA+ friendly-spaces, or community participation from key geographic regions.

>>>>

To organize a more inclusive conference, it is necessary to identify upfront which groups of people are being excluded, the barriers that keep them from active partaking, and targeted strategies to overcome them. 
\textbf{Rule 1} is about embracing all dimensions of diversity and prioritizing the participation of groups that are often marginalized.
However, increasing diversity alone is not enough. \textbf{Rule 2} focuses on how to create a safe and welcoming environment for all the conference attendees. 
Inclusion should start from the organizing team. \textbf{Rule 3} highlights the importance of starting with an inclusive and diverse organizing team, and provides tips on work dynamics.

@@

% Rocío: Main idea: what is diversity and why does it matter? (inequalities)
Diversity encompasses multiple dimensions: age, physical ability, career stage, gender, gender identity, geographic origin, language, neurodiversity, race, religion, sexual orientation, and socioeconomic background, to name a few.
Human diversity should be celebrated and respected in every way. 
Nonetheless, we live in a world with implicit hierarchies along these axes. 
Some statuses (\textit{e.g.}, cisgender, white, male, from North America or Western Europe) hold the privilege of being the defaults around which all systems--including conferences--are consciously and unconsciously built. 
People outside the dominant groups suffer different forms of oppression, like sexism, racism, ableism, homophobia, and transphobia; some people have to deal with several of these on a daily basis.
% While no isolated initiative can drastically alter conference outcomes, building a more diverse and inclusive conference starts by recognizing that these inequalities have systematically excluded whole groups of people from academia and scientific and professional circles. 
Recognizing this systematic exclusion, particularly in our fields and in our scientific or professional communities, will help identify the most marginalized and discriminated subgroups \cite{timperleyHeMoanaPukepuke2020}.
% These are the groups that warrant deliberate efforts that ensure fair inclusion.
As a starting point, identify which groups warrant deliberate efforts to ensure fair inclusion, and determine the contributing factors (e.g. explicit discrimination, participation fees, etc.).
This analysis should guide the vision of diversity and inclusion for your conference and help design strategies to achieve it. 
Express this vision for your conference in a diversity statement. 
Next, use this vision and the set strategies to define measurable indicators and goals of diversity and inclusion (\textit{e.g.}, a gender distribution of your speakers that is representative of the general population, presence of racialized people --especially Black people-- among the head organizers, speakers, and attendees, or participation from key geographic regions). 
These numbers should guide you and help achieve your vision.

% Investing a substantial effort towards the most excluded groups does not mean neglecting the other communities, but will instead ensure equity, guide the vision of diversity for your conference, and help design strategies to achieve it.
% vision
% back to the indicators? 
% realistic but bold (back?)
% be aware and promote awareness
%¡LAS BARRERAS!
%Express the diversity and inclusion vision for your conference by writing a diversity statement. 
% As a starting point, identify which groups are usually unsupported or discriminated against in the community or event of interest, and determine the contributing factors. Next, set measurable indicators of success when organizing a diverse conference. The numbers resulting from these indicators are not the primary goal, and this is not about performative allyship. Instead, these numbers should guide and help hold the organizing team accountable towards these diverse and inclusive goals.

% Rocío: more effort towards including the more excluded
% This may translate into different actions depending on your field, region, or community, \textit{e.g.}, a gender distribution of your speakers that is representative of the general population, presence of racialized people --especially Black people-- among the head organizers, speakers, and attendees, LGBTQIA+ friendly-spaces, or community participation from key geographic regions.
